Uncertainty Literature Review

### 2024-01-16 paper.qmd
added notes

@@

# 4.?? Importance (and unimportance) of Secondary and Meta information
- Specifies uncertainty can be represented by three components attribute (what) position (where) and temporal (when) @Kinkeldey2014
- Studies dealing with uncertainty information typically deal with attribute but rarely position and time @Kinkeldey2014
- 10/44 studies involve multiple types of uncertainty @Kinkeldey2014

>>>>

- if the experiment DOES use noise as a signal, it is often very unclear how the participants should include that in their respose and what would be a valid response from participants (e.g. the likelihood to how much question and the cone of uncertainty questions). separate to the data, uncertainty has its own goal. Is it to impact confidence in the estimate (like a bayesian thing)? to supress signal (like a barely noticiable difference line up plot thing)? to facilitate more efficient decisions (so accounting for risk thing)?

- will it impact their decision at all? there are a couple of papers where you can answer all the questions by just ignoring the uncertainty information because of the way they have set it up. e.g. difference in means when the variance is the same, experiments that check if someone can still get the signal and make sure the uncertainty information isnt in the way.

@@

- I think the dimension of the uncertainty should be considered every time there is aggregation from multiple sources of uncertainty and you want to maintain those sources. You can project the uncertainty down into one dimension if the source information is in of itself unimportant.
# 4.?? Importance (and unimportance) of Secondary and Meta information
- Specifies uncertainty can be represented by three components attribute (what) position (where) and temporal (when) @Kinkeldey2014
- Studies dealing with uncertainty information typically deal with attribute but rarely position and time @Kinkeldey2014
- 10/44 studies involve multiple types of uncertainty @Kinkeldey2014
